---
title: "Rekrutierung"
---

*Deutsche Übersetzung folgt.*

Recruitment is planned to start in **November 2026** and will run for
approximately 12 months across the three participating sites
(Checkpoint Zurich, University Hospital Lausanne (CHUV) and
University Hospital Zurich (USZ)). A target of **800 participants**
is planned in each of the two cohorts, the Swiss HIV Cohort Study
(SHCS) and SwissPrEPared.

```{r setup, include=FALSE}
library(plotly)
library(tidyverse)
library(lubridate)
library(readxl)
```

```{r load-data, include=FALSE}
df <- read_excel("../ADHD_HIV_PrEP_recruitment.xlsx")

df <- df %>%
  mutate(Date = as.Date(Date)) %>%
  arrange(Date)

make_recruitment_plot <- function(data, cohort_name) {
  data_cohort <- data %>%
    filter(Cohort == cohort_name) %>%
    arrange(Date) %>%
    mutate(Total = row_number())

  p <- plot_ly()

  if (nrow(data_cohort) > 0) {
    p <- p %>%
      add_trace(
        data = data_cohort,
        x = ~Date,
        y = ~Total,
        type = "scatter",
        mode = "lines+markers",
        fill = "tozeroy",
        name = paste("Total", cohort_name)
      )
  } else {
    p <- p %>%
      layout(
        annotations = list(
          list(
            text = "Die Rekrutierung hat noch nicht begonnen.<br>Geplanter Start: November 2026",
            xref = "paper", yref = "paper",
            x = 0.5, y = 0.5,
            showarrow = FALSE,
            font = list(size = 16)
          )
        )
      )
  }

  p %>%
    layout(
      title = paste("Rekrutierung im Zeitverlauf —", cohort_name),
      xaxis = list(title = "Datum", type = "date"),
      yaxis = list(title = "Anzahl Teilnehmende", rangemode = "tozero")
    )
}
```

## Swiss HIV Cohort Study (SHCS)

```{r fig-shcs, echo=FALSE}
make_recruitment_plot(df, "SHCS")
```

<!-- Add some space --> <div style="margin-top: 100px;"></div>

## SwissPrEPared

```{r fig-swissprepared, echo=FALSE}
make_recruitment_plot(df, "SwissPrEPared")
```
